Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-17 paper/main.tex
Density of sizes and percentages of the argument to eval.

Analysis of the arguments passed to \eval reveals that XXX are of kind
\c{symbol} (single variables), XXX are \c{language} (an internal R
type roughly corresponding to a single expression), and XXX are
\c{expression} (one or more statements). The remaining arguments are R
values which are returned unchanged.

\mypara{Amount of code loaded by eval.} We use \c{deparse} to turn the
input to \eval into strings and measure the size of that input. The
largest input is \Maxszeval and the median input size is
\Medianszeval. Most inputs are small, less than \SzninefiveRnd
bytes. The average size is \Avgszeval bytes.

>>>>

Analysis of the arguments passed to \eval reveals that \Symbolpercent are of kind
\c{symbol} (single variables), \Languagepercent are \c{language} (an internal R
type roughly corresponding to a single expression), and \Expressionpercent are
\c{expression} (one or more statements), for a total of \Codepercent of the \eval calls. The remaining arguments are R
values which are returned unchanged. \NOTE{closures are forced. (but there are nearly none in our dataset)}

\mypara{Amount of code loaded by eval.} We use \c{deparse} to turn the
resolved input to \eval into strings and measure the size of that input. The
largest input is \Maxszeval and the median input size is
\Medianszeval. Most inputs are small, less than \SzninefiveRnd
characters. The average size is \Avgszeval characters. 
Figure~\ref{fig:sizedistribution} shows the distribution of sizes.

\begin{figure}[h]
	%\centering 
	\includegraphics[width=\textwidth]{size_loaded_distribution}
	\caption{Distribution of the sized of the expressions loaded by \eval.} \label{fig:sizedistribution}
\end{figure}
